IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
nits

Indeed, by rephrasing LIO in terms of our framework, we simplified
LIO's treatment of exceptions.
%
LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Breeze}.
%
In particular, the label of an exception was set to the current label
at the time of the throw, and used by a custom catch construct to
raise the current label, thereby preventing leaks due exceptional
control flows.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the current label, see
Section~\ref{sec:extensions:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch (a consequence of
defining \verb|LIO| using a State monad).
%
Moreover, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
By using isolated tasks, and thus treating the current label (and
clearance) as global, the underlying Haskell exception system can be
used directly: exceptional control flow does not affect IFC.

>>>>

Indeed, by rephrasing LIO in terms of our framework, we simplified
LIO's treatment of exceptions.
%
LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%
In particular, the label of an exception was set to the current label
at the time of the throw, and used by a custom catch construct to
raise the current label, thereby preventing leaks due exceptional
control flows.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the current label, see
Section~\ref{sec:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch (a consequence of
defining \verb|LIO| using a State monad).
%
Moreover, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
By using isolated tasks, and thus treating the current label (and
clearance) as global, the underlying Haskell exception system can be
used directly: exceptional control flow does not affect IFC.
